### 2015-05-20 docs/prelim_analysis.Rmd
updates doc with new results and text

---
output:
  pdf_document:
    fig_caption: true
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
---

# Preliminary community synchrony analysis

A couple comments from Claire:

1. In the absence of environmental stochasticity, species fluctuations are not necessarily independent. 
For example in a zero sum game with ecologically equivalent species (Hubbell's neutral model), species fluctuate randomly but they are not independent since the sum is constrained. If there are only two species their fluctuations are necessarily negatively correlated, because the increase in one species must be compensated by a decrease in the other. In a non-neutral model where species have stable equilibrium abundance there are also non independent fluctuations due to species interactions. In competitive communities fluctuations would most of the time have negative correlations overall, but sometimes they can be positive overall.

2. I'm not entirely clear here: null with respect to what? Species interactions, demographic stochasticity and environmental stochasticity can all affect synchrony?

3. Could you show the absolute values, either with three bars per plot, or with a black line that is not at zero but at its unperturbed synchrony value? OK, I see the absolute values in table 1, the differences between sites are quite large compared to the effects of demographic and environmental stochasticities - but it should still be visible. Does this suggest that environmental and demographic stochasticities are minor explanatory variables for community synchrony? What is, then? Diversity?

4. In principle, could the signs of the effects of demographic stochasticity and environmental stochasticity be predicted? For demographic stochasticity, see comment by table 1. For environmental stochasticity: could you quantify the synchrony of species responses to the environment from the synchrony of the intercepts?

5. We could compute the synchrony expected under independent fluctuations: 
$$\text{E}(\phi_{r}) = \frac{ \sum_{i=1}^{N}{\sigma_{i}^2} } { \left(\sum_{i=1}^{N}{\sigma_{i}} \right)^2 }.$$
We could expect demographic stochasticity to tend towards this value: the sign of the effect of demographic stochasticity should be $\text{E}(\phi_{r}) - \phi_{r}$, where $\phi_{r}$ is the observed synchrony of per capita growth rates; removal should be the opposite - does that work?

## Calculate expected and observed sychrony
Under the assumption of independent fluctuations in species' per capit growth rates, we can calculate expected synchrony as:

$$\text{E}(\phi_{r}) = \frac{ \sum_{i=1}^{N}{\sigma_{i}^2} } { \left(\sum_{i=1}^{N}{\sigma_{i}} \right)^2 }$$

where $\sigma_{i}$ is the standard deviation of species $i$'s per capita growth rate through time.

```{r get_synchs, echo=FALSE, include=TRUE}
out <- get_comm_synchrony(ts_data = ks_data)
obs_synch <- round(as.numeric(out$pgr_synchrony[1]), 2)
exp_synch <- round(out$pgr_expected_synch_ind_flucts, 2)
exp_demo_effect <- exp_synch - obs_synch
print(out$pgr_synchrony)
print(out$pgr_expected_synch_ind_flucts)
```

```{r sign_text, echo=FALSE}
if(sign(exp_demo_effect)==-1){
  sign_text <- "decrease"
  remove_text <- "increase"
}
if(sign(exp_demo_effect)==1){
 sign_text <- "increase"
 remove_text <- "decrease" 
}
```

So, $\text{E}(\phi_{r})$ = `r exp_synch` and $\phi_{r}$ = `r obs_synch`. Which means the expected effect of demographic stochasticity [$\text{E}(\sigma_{d}) = \text{E}(\phi_{r}) - \phi_{r}$] is `r exp_demo_effect`. So, based on the sign of $\text{E}(\sigma_{d})$ we expect demographic stochasticity to `r sign_text` synchrony among species' per capita growth rates. Thus, removing demographic stochasticity should `r remove_text` synchrony in our population model simulations.

Here are the results for both Kansas and Idaho:

```{r get_all_synch, echo=FALSE, include=TRUE}
out_ks <- out
out_id <- get_comm_synchrony(ts_data = id_data)
out_mt <- get_comm_synchrony(ts_data = mt_data)
out_nm <- get_comm_synchrony(ts_data = nm_data)
out_az <- get_comm_synchrony(ts_data = az_data)
```

```{r synchrony_table, echo=FALSE, include=TRUE, results='asis'}
get_table_metrics <- function(output){
  tmp <- output
  exp_tmp <- round(tmp$pgr_expected_synch_ind_flucts, 2)
  obs_tmp <- round(as.numeric(tmp$pgr_synchrony[1]), 2)
  demo_tmp <- exp_tmp - obs_tmp
  return(c(obs_tmp, exp_tmp, demo_tmp))
}

synch_cap <- "Observed and expected synchrony among species' per capita growth rates and expected effect of demographic stochasticity on observed synchrony. Species richness values reflect the number of species analyzed from the community, not the actual richness."
print(xtable(table_data, caption = synch_cap),
      caption.placement="top",
      include.rownames = F, 
      sanitize.colnames.function = identity)
```

```{r time_series_fig, echo=FALSE, include=TRUE, fig.height=7, fig.cap="Observed time series of mean percent cover (averaged over quadrats for each year) and per capita growth rates for each species at each site."}
out_ks$percent_cover$site <- "Kansas"
out_id$percent_cover$site <- "Idaho"
out_mt$percent_cover$site <- "Montana"
out_nm$percent_cover$site <- "New Mexico"
out_az$percent_cover$site <- "Arizona"
cover_data <- rbind(out_ks$percent_cover, out_id$percent_cover,
                    out_mt$percent_cover, out_nm$percent_cover, 
                    out_az$percent_cover)

out_ks$growth_rates$site <- "Kansas"
out_id$growth_rates$site <- "Idaho"
out_mt$growth_rates$site <- "Montana"
out_nm$growth_rates$site <- "New Mexico"
out_az$growth_rates$site <- "Arizona"
pgr_data <- rbind(out_ks$growth_rates, out_id$growth_rates,
                  out_mt$growth_rates, out_nm$growth_rates, 
                  out_az$growth_rates)
all_spp <- unique(pgr_data$species)
color_match <- data.frame(species = all_spp,
                          color = brewer.pal(11,"Paired"))
pgr_data <- merge(pgr_data, color_match, by = "species")
cover_data <- merge(cover_data, color_match, by="species")

cover_plot <- ggplot(data=cover_data, aes(x=(year+1900), y=tot_cover, color=color))+
                geom_line()+
                geom_point()+
                facet_grid(site~., scales = "free_y")+
                guides(color=FALSE)+
                ylab("Mean Percent Cover")+
                xlab("Year")+
                scale_color_manual(values = brewer.pal(11,"Paired"))

pgr_plot <- ggplot(data=pgr_data, aes(x=(year+1900), y=pgr, color=color))+
              geom_line()+
              geom_point()+
              facet_grid(site~., scales = "free_y")+
              guides(color=FALSE)+
              ylab("Per Capita Growth Rate")+
              xlab("Year")+
              scale_color_manual(values = brewer.pal(11,"Paired"))
full_plot <- grid.arrange(cover_plot, pgr_plot, ncol=2)
```

# Methods
## Study sites and species
We use the exact same data as presented in Chu and Adler (2015). From their paper:

@@

## Analytical approach
While the observational data allows to directly calculate species synchrony within the community, it is impossible to isolate the contributions of demographic and environmental stochasticity on species synchrony based on the data alone. So we now turn to a empirically-based modeling approach where we can turn demographic and environmental stochasticity on/off. To our knowledge, Integral Projection Models (IPMs) are the only tools available that allow us to isolate sources of stochasticity. For example, individual-based models require demographic stochasticity, making it impossible to isolate the effect of environmental stochasticity alone.

@@

## Statistical models for survival, growth, and recruitment
### Survival and growth
We modeled survival probability and growht on individual genets as a function of genet size, the crowding experienced by the focal genet from both hetero and conspecific genets in its neighborhood (described below), temporal varation among years, and spatial variation among quadrat groups. Groups are sets of quadrats located in close proximity within a pasture or grazing exclosure).

@@

$$
w_{ijm,t} = \sum_k e^{-\delta_{jm}d_{ijkm,t}^{2}}u_{km,t}.
$$

@@

## Integral projection models (IPM)
We built an environmentally and demographically stochastic integral projection model (IPM), where either environmental or demographic stochasticity can be turned off. Our IPM follows the specification of Chu and Adler (2015) where the population of species _j_ is a density function $n(u_{j},t)$ giving the density of sized-_u_ genets at time _t_. Genet size is on the natural log scale, so that $n(u_{j},t)du$ is the number of genets whose area (on the arithmetic scale) is between $e^{u_{j}}$ and $e^{u_{j}+du}$. So, the density function for any size _v_ at time $t+1$ is

$$
n(v_{j},t+1) = \int_{L_{j}}^{U_{j}} k_{j}(v_{j},u_{j},\bar{\bold{w_{j}}}(u_{j}))n(u_{j},t)
$$

@@

$$
k_{j}(v_{j},u_{j},\bar{\bold{w_{j}}}) = S_j(u_j, \bar{\bold{w_{j}}}(u_{j}))G_j(v_{j},u_{j},\bar{\bold{w_{j}}}(u_{j})) + R_j(v_{j},u_{j},\bar{\bold{w_{j}}}),
$$

@@

>>>>

---
output:
  pdf_document:
    fig_caption: true
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
---
# Drivers of species synchrony in real communities
*Andrew Tredennick, Peter Adler, Claire de Mazancourt, Michele Loreau, and Stephen Ellner*

Quick summary
-------------
1. __Question__. How (a)synchronous are species population dynamics in natural communities, and what determines the degree of synchrony among species? Of particular interest to us, do species' responses to environmental fluction increase or decrease population synchrony?

2. __Data__. Five longterm demographic datasets from semi-arid North American grasslands. All species coexist stabley, yet are similar -- they are all perennial grasses.

3. __Analysis__. (a) Calculate community synchrony from the observed time series using an established metric, and compare this to expectation from theory. (b) Use IPMs with environmental or demographic stochasticity turned on/off to quantify the relative contribution of each to community synchrony.

4. __Initial conclusions__. Species' responses to environmental fluctuations tend to synchronize population dynamics: at four of the five sites removing environmental fluctuations decreased community synchrony. However, even with environmental fluctuations present, populations were not completely synchronized. This implies that niche differences among these species remain strong even as they respond similarly to environmental conditions.

Introduction
------------
Asynchrony in population dynamics among co-occuring plant species stabilizes ecosystem-level properties like annual biomass production (Hector et al. 2010, Loreau and de Mazancourt 2013, de Mazancourt et al. 2013, Hautier et al. 2014). Species-specific responses to environmental conditions, in particular, can stabilize ecosystem properties even as environmental forcings fluctuate through time. Such asynchrony of species dynamics in response to the environment has the potential to buffer ecosystems subjected to an increasingly variable climate. Thus, the extent to which natural communities exhibit asynchronous dynamics determines, in part, their ability to cope with interannual climate extremes that are projected to become more common.

Theory suggests that community synchrony is driven by a combination of internal and external forces. Internal to the community, demographic stochasticity can induce asynchronous dynamics when species tend to fluctuate independently in a constant environment (Loreau and de Mazancourt 2008). However, species live in non-constant environments that act as strong external drivers of community dynamics. Environmental variability can induce asynchronous dynamics when species' responses to environmental conditions are temporally uncorrelated. When species respond similarly to environmental conditions, community dynamics become more synchronized (Gonzalez and Loreau 2009, Loreau and de Mazancourt 2008).

It is impossible to draw inference on the relative contribution of demographic and environmental stochasticity on synchrony based on empirical estimates alone, so our analysis involves two steps.  First, we will use longterm datasets from five North American grasslands (Fig. 1; Chu and Adler 2015) to calculate community synchrony. Second, we will fit multispecies population models to the data for dominant species to evaluate the relative contribution of species' environmental responses and demographic stochasticity to community synchrony. Sparse data on sub-dominant species constrained model fitting to dominant species that account for ##% - ##% of local plant abundance at their respective sites. Our focus is on temporal trends of per capita growth rates becuase these best reflect the short-term responses of populations to environmental conditions that fluctuate on annual time scales (Loreau and de Mazancourt 2008).

What is expected by theory?[^devel]
---------------------------
[^devel]: Note that this is still in development...so some of it may be wrong.

Loreau and de Mazancourt (2008) derived a statistic to measure community-wide synchrony of per capita population growth rates:

\begin{equation}
\phi_r = \frac{\sigma^{2}_{T}}{(\sum_{i}\sigma_{r_{i}})^{2}}
\end{equation}

where $\sigma_{r_{i}}$ is the temporal variance of species *i*'s per capita population growth rate ($r_i$) and $\sigma^{2}_{T}$ is the temporal variance of the aggregate community-level growth rate. The statistic is bounded at 0 and 1, where 0 indicates perfect asynchrony and 1 indicates perfect synchrony. When applied to a neutral model where species have perfect niche overlap but have independent demographic and environmental fluctuations through time,  expected synchrony ($\phi_r$) is defined as:

\begin{equation}
\phi_r = \frac{\sigma^{2}_{c} + \sigma^{2}_{e} + \sigma^{2}_{d}/(SN)}{[(1/S)(\sum_{i}\sqrt{\sigma^{2}_{c} + \sigma^{2}_{e} + \sigma^{2}_{d}/(N)})]^2}
\end{equation}

where $\sigma^{2}_{c}$ is the temporal variance of per capita population growth rates due to regulation of community size (density-dependence), $\sigma^{2}_{e}$ is environmental variance, and $\sigma^{2}_{d}$ is demographic variance. *S* is the species richness of the focal community and *N* is the harmonic temporal mean of either the entire community (no subscript in numerator) or species *i* (with subscript in denominator).

Loreau and de Mazancourt show that when demographic stochasticity is weak relative to community regulation and environmental forcing ($\sigma^{2}_{c}+\sigma^{2}_{e} >> \sigma^{2}_{d}/N_i$), $\phi_r \approx 1$ meaning species are expected to fluctuate synchronously. At the other limit, where environmental forcing and community regulation are strong relative to demographic stochasticity ($\sigma^{2}_{c}+\sigma^{2}_{e} << \sigma^{2}_{d}/N_i$), species are expected to fluctuate independently, and $\phi_r \approx 1/S$ or:

\begin{equation}
\phi_{r} = \frac{ \sum_{i=1}^{N}{\sigma_{i}^2} } { \left(\sum_{i=1}^{N}{\sigma_{i}} \right)^2 }.
\end{equation}

Based on the above theory, we expect synchrony in a community where only demographic stochasticity is operating on top of independent fluctuations to be $1/S$.

Data and Methods
----------------
## Study sites and species
We use the exact same data as presented in Chu and Adler (2015). From their paper:

@@

## Analytical approach
While the observational data allows us to directly calculate species synchrony within the community, it is impossible to isolate the contributions of demographic and environmental stochasticity on species synchrony based on the data alone. So we now turn to a empirically-based modeling approach where we can turn demographic and environmental stochasticity on/off. To our knowledge, Integral Projection Models (IPMs) are the only tools available that allow us to isolate sources of stochasticity. For example, individual-based models require demographic stochasticity, making it impossible to isolate the effect of environmental stochasticity alone.

@@

## Statistical models for survival, growth, and recruitment
### Survival and growth
We modeled survival probability and growht on individual genets as a function of genet size, the crowding experienced by the focal genet from both heterospecific and conspecific genets in its neighborhood (described below), temporal varation among years, and spatial variation among quadrat groups. Groups are sets of quadrats located in close proximity within a pasture or grazing exclosure).

@@

\begin{equation}
w_{ijm,t} = \sum_k e^{-\delta_{jm}d_{ijkm,t}^{2}}u_{km,t}.
\end{equation}

@@

### Recruitment
We model recruitment as a function of plot-level cover, temporal varation among years, and spatial variation among quadrat groups.

## Integral projection models (IPM)
### Model structure
We built an environmentally and demographically stochastic integral projection model (IPM), where either environmental or demographic stochasticity can be turned off. Our IPM follows the specification of Chu and Adler (2015) where the population of species _j_ is a density function $n(u_{j},t)$ giving the density of sized-_u_ genets at time _t_. Genet size is on the natural log scale, so that $n(u_{j},t)du$ is the number of genets whose area (on the arithmetic scale) is between $e^{u_{j}}$ and $e^{u_{j}+du}$. So, the density function for any size _v_ at time $t+1$ is

\begin{equation}
n(v_{j},t+1) = \int_{L_{j}}^{U_{j}} k_{j}(v_{j},u_{j},\bar{\bold{w_{j}}}(u_{j}))n(u_{j},t)
\end{equation}

@@

\begin{equation}
k_{j}(v_{j},u_{j},\bar{\bold{w_{j}}}) = S_j(u_j, \bar{\bold{w_{j}}}(u_{j}))G_j(v_{j},u_{j},\bar{\bold{w_{j}}}(u_{j})) + R_j(v_{j},u_{j},\bar{\bold{w_{j}}}),
\end{equation}

@@

### Model simulations
Our interest is in the (de)synchronizing effects of either demographic or environmental stochasticity. To look at these effects, we run three types of model simulations: (1) demographic stochasticity only, (2) environmental stochasticity only, and (3) both. Environmental stochasticity is implemented by drawing random year effects for the vital rate regressions. We can model a constant environment by simply using vital rate regressions with mean coefficient values. To include demographic stochasticity we treat survival as a binomial process and recruitment as a poisson process in the IPM[^stoch]. See Figure 2 for example model runs.

[^stoch]: This is the crux of the matter here, we need to implement the Poisson approximation at the iteration matrix stage.

Results
-------
## Observed and expected synchrony
Our first task was to calculate the observed and expected community synchrony at each of our study sites. Observed synchrony ($\phi_r$) is calculate using equation 1 and expected synchrony ($\text{E}(\phi_r)$) is simply $1/S$ or equation 3. Expected synchrony under indpendent fluctuations is lower than the observed synchrony at every site (Table 1). This implies that demographic stochasticity is weak relative to community regulation and environmental forcing ($\sigma^{2}_{c}+\sigma^{2}_{e} >> \sigma^{2}_{d}/N_i$). Thus, some combination of density-dependence (species interactions) and environmental forcing are synchronizing population dynamics. To isolate those effects, we turn to our simulation results from the IPMs.

```{r get_all_synch, echo=FALSE, include=TRUE}
out_ks <- get_comm_synchrony(ts_data = ks_data)
out_id <- get_comm_synchrony(ts_data = id_data)
out_mt <- get_comm_synchrony(ts_data = mt_data)
out_nm <- get_comm_synchrony(ts_data = nm_data)
out_az <- get_comm_synchrony(ts_data = az_data)
```

```{r synchrony_table, echo=FALSE, include=TRUE, results='asis', message=FALSE}
get_table_metrics <- function(output){
  tmp <- output
  exp_tmp <- round(tmp$pgr_expected_synch_ind_flucts, 2)
  obs_tmp <- round(as.numeric(tmp$pgr_synchrony[1]), 2)
  demo_tmp <- exp_tmp - obs_tmp
  return(c(obs_tmp, exp_tmp, demo_tmp))
}

synch_cap <- "Observed and expected synchrony among species' per capita growth rates and expected effect of demographic stochasticity on observed synchrony. Species richness values reflect the number of species analyzed from the community, not the actual richness."
print(xtable(table_data, caption = synch_cap),
      caption.placement="top",
      include.rownames = F, 
      sanitize.colnames.function = identity,
      comment=FALSE)
```

```{r time_series_fig, echo=FALSE, include=TRUE, fig.height=7, fig.cap="Observed time series of mean percent cover (averaged over quadrats for each year) and per capita growth rates for each species at each site."}
# out_ks$percent_cover$site <- "Kansas"
# out_id$percent_cover$site <- "Idaho"
# out_mt$percent_cover$site <- "Montana"
# out_nm$percent_cover$site <- "New Mexico"
# out_az$percent_cover$site <- "Arizona"
# cover_data <- rbind(out_ks$percent_cover, out_id$percent_cover,
#                     out_mt$percent_cover, out_nm$percent_cover, 
#                     out_az$percent_cover)
# 
# out_ks$growth_rates$site <- "Kansas"
# out_id$growth_rates$site <- "Idaho"
# out_mt$growth_rates$site <- "Montana"
# out_nm$growth_rates$site <- "New Mexico"
# out_az$growth_rates$site <- "Arizona"
# pgr_data <- rbind(out_ks$growth_rates, out_id$growth_rates,
#                   out_mt$growth_rates, out_nm$growth_rates, 
#                   out_az$growth_rates)
# all_spp <- unique(pgr_data$species)
# color_match <- data.frame(species = all_spp,
#                           color = brewer.pal(11,"Paired"))
# pgr_data <- merge(pgr_data, color_match, by = "species")
# cover_data <- merge(cover_data, color_match, by="species")
# 
# cover_plot <- ggplot(data=cover_data, aes(x=(year+1900), y=tot_cover, color=color))+
#                 geom_line()+
#                 geom_point()+
#                 facet_grid(site~., scales = "free_y")+
#                 guides(color=FALSE)+
#                 ylab("Mean Percent Cover")+
#                 xlab("Year")+
#                 scale_color_manual(values = brewer.pal(11,"Paired"))
# 
# pgr_plot <- ggplot(data=pgr_data, aes(x=(year+1900), y=pgr, color=color))+
#               geom_line()+
#               geom_point()+
#               facet_grid(site~., scales = "free_y")+
#               guides(color=FALSE)+
#               ylab("Per Capita Growth Rate")+
#               xlab("Year")+
#               scale_color_manual(values = brewer.pal(11,"Paired"))
# full_plot <- grid.arrange(cover_plot, pgr_plot, ncol=2)
```

## Effect of removing demographic and environmental stochasticity
At four of our five study areas, the presence of environmental stochasticity via random year effects on vital rate regressions increased community synchrony of per capita population growth rates (Figure 1). Only at the Montana site (Northern Mixed Prairie) did incorporating species' responses to environmental conditions decrease community synchrony. However, even with similar responses to environmental conditions, community synchrony did not reach 1 at any of the sites. Thus, there remains sufficiently strong temporal niche differences to drive the community away from perfect sychrony.

*NOTE: we have not dealt with species interactions yet...*

```{r read_data, echo=FALSE}
output_list <- readRDS("../results/ipm_simulation_lists.RDS")
mlist <- melt(output_list)
```

```{r get_synchs, echo=FALSE, fig.cap="Results from IPM simulations with difference sources of stochasticity present/absent at each site. DEMO = demographic stochasticity only; ENV = environmental stochasticity only; ENVDEMO = both demograhpic and environmental stochasticity.", fig.width=6}
colnames(mlist)[1:3] <- c("year", "species", "cover")
mlist <- subset(mlist, year>500)
sites <- unique(mlist$L1)
sims <- unique(mlist$L2)
pgr_list <- list()
for(dosite in sites){
  tmp_data <- subset(mlist, L1==dosite)
  if(dosite=="Idaho"){
    tmp_data <- subset(tmp_data, species!="ARTR")
  }
  within_site_list <- list()
  for(dosim in sims){
    tmpsim <- subset(tmp_data, L2==dosim)[c("year", "species", "cover")]
    tmpsynch <- get_ipm_synchrony(tmpsim)
    tmp_pgr_synch <- as.numeric(tmpsynch$pgr_synchrony["obs"])
    within_site_list[[dosim]] <- tmp_pgr_synch
  }
  pgr_list[[dosite]] <- within_site_list
}
pgr_synch <- melt(pgr_list)

ggplot(pgr_synch, aes(x=L2, y=value, fill=L2))+
  geom_bar(stat="identity", position=position_dodge(0.9), color="grey")+
  facet_wrap("L1", scales="free_x")+
  scale_fill_manual(values = c("grey45", "steelblue", "slateblue4"))+
  guides(fill=FALSE)+
  scale_y_continuous(limits=c(0,1))+
  xlab("Source of stochasticity")+
  ylab("Species synchrony")

```

```{r niches, echo=FALSE}
# niche_diff <- data.frame(site=sites,
#                          ND = c(0.58, 0.59, 0.66, 0.69, 0.68))
# pgr_subs <- subset(pgr_synch, L2!="ENVDEMO")
# pgr_cast <- dcast(pgr_subs, L1~L2, value.var = "value")
# synch_diff <- ddply(pgr_cast, .(L1), summarise,
#                     value = ENV-DEMO)
# niche_synch <- merge(niche_diff, synch_diff, by.x="site", by.y="L1")
# ggplot(niche_synch, aes(x=ND, y=value))+
#   geom_point(size=5)+
#   ylab("Community synchrony")
```

Theory predicts that demographic stochasticty is the only force that, in isolation, can desynchronize population dynamics. However, theory also predicts that demographic stochasticity is likely unable to counteract the synchronizing effect of environmental forces. Our results support this prediction in the cases where environmental stochasticity is a synchronizing force (compare ENV and ENVDEMO bars in Figure 1).

\newpage

Additional Figures
------------------
```{r time_series, echo=FALSE, fig.cap="Example time series from the simulations."}
ggplot(mlist, aes(x=year, y=(cover*100), color=species))+
  geom_line()+
  facet_grid(L1~L2, scale="free")
```
